### 2022-02-19 data-science/p3/submission.Rmd
Rename nanodegree folders

### Effect of acids on wine quality
```{r echo=FALSE, Plot_One}
grid.arrange(ggplot(data = df, aes(x = quality, y = fixed.acidity,
                                   fill = quality)) + 
               ggtitle('Fixed Acidity in Different Wine Quality') +
               ylab('Fixed Acidity (g/dm^3)') +
               xlab('Quality') +
               geom_boxplot(),
             ggplot(data = df, aes(x = quality, y = volatile.acidity,
                                   fill = quality)) +
               ggtitle('Volatile Acidity in Different Wine Quality') +
               ylab('Volatile Acidity (g/dm^3)') +
               xlab('Quality') +
               geom_boxplot(), 
             ggplot(data = df, aes(x = quality, y = citric.acid,
                                   fill = quality)) +
               ggtitle('Citric Acidity in Different Wine Quality') +
               ylab('Citric Acid (g/dm^3)') +
               xlab('Quality') +
               geom_boxplot(), 
             ggplot(data = df, aes(x = quality, y = pH,
                                   fill = quality)) +
               ggtitle('pH in Different Wine Quality') +
               ylab('pH') +
               xlab('Quality') +
               geom_boxplot())

@@

### Effect of Alcohol on Wine Quality
```{r echo=FALSE, Plot_Two}
ggplot(data = df, aes(x = quality, y = alcohol,
                      fill = rating)) +
  geom_boxplot() +
  ggtitle('Alcohol Levels in Different Wine Qualities') +
  xlab('Quality') +
  ylab('Alcohol (% volume)')
```

@@

### Plot Three
```{r echo=FALSE, Plot_Three}
ggplot(data = subset(df, rating != 'average'),
       aes(x = volatile.acidity, y = alcohol,
                      color = rating)) +
  geom_point() +
  ggtitle('Alcohol vs. Volatile Acidity and Wine Quality') +
  xlab('Volatile Acidity (g / dm^3)') +
  ylab('Alcohol (% volume)')
```

>>>>

### Plot 1: Effect of acids on wine quality
```{r echo=FALSE, Plot_One}
grid.arrange(ggplot(data = df, aes(x = quality, y = fixed.acidity,
                                   fill = quality)) + 
               ylab('Fixed Acidity (g/dm^3)') +
               xlab('Quality') +
               geom_boxplot(),
             ggplot(data = df, aes(x = quality, y = volatile.acidity,
                                   fill = quality)) +
               ylab('Volatile Acidity (g/dm^3)') +
               xlab('Quality') +
               geom_boxplot(), 
             ggplot(data = df, aes(x = quality, y = citric.acid,
                                   fill = quality)) +
               ylab('Citric Acid (g/dm^3)') +
               xlab('Quality') +
               geom_boxplot(), 
             ggplot(data = df, aes(x = quality, y = pH,
                                   fill = quality)) +
               ylab('pH') +
               xlab('Quality') +
               geom_boxplot())

@@

### Plot 2: Effect of Alcohol on Wine Quality
```{r echo=FALSE, Plot_Two}
ggplot(data = df, aes(x = quality, y = alcohol,
                      fill = rating)) +
  geom_boxplot() +
  ggtitle('Alcohol Levels in Different Wine Qualities') +
  xlab('Quality') +
  ylab('Alcohol (% volume)')
```

@@

### Plot 3: What makes good wines, good, and bad wines, bad?
```{r echo=FALSE, Plot_Three}
ggplot(data = subset(df, rating != 'average'),
       aes(x = volatile.acidity, y = alcohol,
                      color = rating)) +
  geom_point() +
  ggtitle('Alcohol vs. Volatile Acidity and Wine Quality') +
  xlab('Volatile Acidity (g / dm^3)') +
  ylab('Alcohol (% volume)')
```
